\section{Student-Supervisor Agreement}

\small{

Our signatures below indicate that we have read and understood the following agreement, and that all parties will do their best to live up to the word as well as the spirit of it.

We agree to meet at least once every two weeks for at least half an hour to discuss progress, plans, and problems that have arisen.
Before each meeting, the group will prepare a brief progress report that will form the basis for the discussions at the meeting.

If a meeting has to be canceled by the supervisor, he should advise the group as early as possible.
If a student cannot attend a meeting, she/he should advise members of the group as well as the supervisor as early as possible.

Both the supervisor and the students will:
\begin{itemlist}
	\item Inform themselves of the course expectations and grading procedure.
\end{itemlist}

The supervisor will:
\begin{itemlist}
	\item Provide regular guidance, mentoring, and support for his design project group,
	\item Take an active role in evaluating the work and performance of the students' by completing the supervisor's portion of the grading forms for each course deliverable expediently.
	\item Return a photocopy of the completed grading evaluation forms to the appropriate section administrator in a timely fashion.
	\item Be aware of the aims and processes of the course as outlined in the Supervisor's Almanac.
\end{itemlist}


\vfill \hrule Jason Anderson \hfill Date \hspace{1.5in}
\vfill \hrule Neil Isaac \hfill Date \hspace{1.5in}
\vfill \hrule Keyi Shi \hfill Date \hspace{1.5in}

}

